Manifold Destiny - or how to rig an election

### 2024-01-21 presentation.qmd
paperprespol
break

Election outome
```{r, echo=F}
sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
```

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$

Election outome
```{r, echo=F}
sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
```

@@

Election outome
```{r, echo=F}
sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
```

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$

Election outome
```{r, echo=F}
sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
```

>>>>

Election outome 
```{r, echo=F}
#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
```

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex3)),3))`$
\end{equation*}

Election outome
```{r, echo=F}
#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pri_int_ex3))),c(0,1))
```

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex3)),3))`$

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pos_int_ex3))),c(0,1))
```
```{r}
knitr::knit_exit()
```
